---
title: "Getting started with shinyChatR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with shinyChatR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(shinyChatR)
```

# Database connection for storing chat data

If you are using a database connection to store the chat messages, you will need to initialize the database table before using the chat module. The following example shows an example how to do this using the `DBI` and `RSQLite` packages. Replace `db_file` with the path to your database file. The data will be saved in the table `chat_data`. 

```{r}
library(DBI)
library(RSQLite)

db_file <- "path_to_your_database_file"
conn <- dbConnect(RSQLite::SQLite(), db_file)

# initiate chat table
df <- data.frame(rowid = numeric(),
                 user = character(),
                 text = character(),
                 time = double())
dbWriteTable(conn, "chat_data", df)
```

Now you can add the chat module to your app:

```{r}
ui <- fluidPage(
  chat_ui("test")
)

server <- function(input, output, server) {
  chat_server("test", db_connection = conn,
              db_table_name = "chat_data",
              chat_user = "user1")
}

# Run the application
shinyApp(ui = ui, server = server)
```

## Reactive user name

This example show how the user name can be stored in a reactive. Here the user specifies the name in a textInput field. 
```{r}
ui <- fluidPage(

  fluidRow(
    column(width = 6,
           # Here the user specifies the user name
           textInput("user", "Enter User Name"),
           br(),
           # add chat ui elements
           chat_ui("test_reactive"),
    )
  )
)
```

Then, in the server the user name is save in the reactive `user_rv`. This reactive can be passed into the argument `chat_user`.
```{r}
server <- function(input, output, server) {

  # save user name in reactive
  user_rv <- reactive({input$user})

  # corresponding server part for id test_reactive
  chat_server("test_reactive", db_connection = conn,
              db_table_name = "chat_data",
              chat_user = user_rv
  )
}
```


# RDS file for storing chat data

Also the rds file first needs to be initialized.

```{r}
df <- data.frame(rowid = numeric(),
                 user = character(),
                 text = character(),
                 time = double())

test_rds <- "path_to_rds_file.rds"
saveRDS(df, test_rds)
```

Now you can add the chat module to your app:

```{r}
test_rds <- "path_to_rds_file.rds"

ui <- fluidPage(
  chat_ui("test2")
)

server <- function(input, output, server) {
  chat_server("test2", 
              rds_path = test_rds,
              chat_user = "user2")
}

# Run the application
shinyApp(ui = ui, server = server)
```

